\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-11-21 doc/USER_MANUAL/manual_SPECFEM3D.tex
improved the paragraph about single precision in the manual

\begin{description}
\item [{\texttt{LOCAL\_PATH\_IS\_ALSO\_GLOBAL}}] Set to \texttt{.false.}
on most cluster applications. For reasons of speed, the (parallel)
distributed database generator typically writes a (parallel) database for the solver on the
local disks of the compute nodes. Some systems have no local disks,
e.g., BlueGene or the Earth Simulator, and other systems have a fast
parallel file system, in which case this flag should be set to \texttt{.true.}.
Note that this flag is not used by the database generator or the solver; it is
only used for some of the post-processing.
\end{description}
The package can run either in single or in double precision. The default
is single precision mode because this requires exactly half as much
memory. Select your preference by selecting the appropriate setting
in the \texttt{constants.h} file:

@@

\begin{description}
\item [{\texttt{CUSTOM\_MPI\_TYPE}}] Set to \texttt{MPI\_REAL} for single
precision and \texttt{MPI\_DOUBLE\_PRECISION} for double precision.
\end{description}
On a new system, it is definitely worth experimenting with single
versus double precision simulations to determine which is faster.
Note that on many current processors (e.g., Intel, AMD, IBM Power),
single precision calculations are often significantly faster; the
difference can typically be 10\% to 25\%. It is therefore often worth
using single precision if you can. We recommend running the same calculation
once in single precision and in double precision on your system and
then comparing the seismograms. If they are identical, you should probably
select single precision for your future runs.\\

>>>>

\begin{description}
\item [{\texttt{LOCAL\_PATH\_IS\_ALSO\_GLOBAL}}] Set to \texttt{.false.}
on most cluster applications. For reasons of speed, the (parallel)
distributed database generator typically writes a (parallel) database for the solver on the
local disks of the compute nodes. Some systems have no local disks,
e.g., BlueGene or the Earth Simulator, and other systems have a fast
parallel file system, in which case this flag should be set to \texttt{.true.}.
Note that this flag is not used by the database generator or the solver; it is
only used for some of the post-processing.
\end{description}
The package can run either
in single or in double precision mode. The default is single precision
because for almost all calculations performed using the spectral-element method
using single precision is sufficient and gives the same results (i.e. the same seismograms);
and the single precision code is faster and requires exactly half as much memory.
Select your preference by selecting the appropriate setting in the \texttt{constants.h} file:

@@

\begin{description}
\item [{\texttt{CUSTOM\_MPI\_TYPE}}] Set to \texttt{MPI\_REAL} for single
precision and \texttt{MPI\_DOUBLE\_PRECISION} for double precision.
\end{description}
On many current processors (e.g., Intel, AMD, IBM Power), single precision calculations
are significantly faster; the difference can typically be 10\%
to 25\%. It is therefore better to use single precision.
What you can do once for the physical problem you want to study is run the same calculation in single precision
and in double precision on your system and compare the seismograms.
If they are identical (and in most cases they will), you can select single precision for your future runs.\\
